Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-07-21 ehp_revision/response_to_reviewers.Rmd

Here is the text where we discuss this point in the original manuscript:

> **Text in original manuscript:**
"There was some evidence that our primary rainfall metric may tend to
underestimate rainfall totals in storms with extremely high rainfall, based on
a few heavy-rainfall storms in Harris County, TX, Mobile County, AL, Charleston
County, SC, and Wake County, NC (Figure 2)."

> **Text in original manuscript:**
"The rainfall data are generally well-correlated with ground-based observations,
but may sometimes underestimate very high rainfall values (Figure 2). When
rainfall data is used to create binary exposure classifications, this
disagreement is unlikely to influence results, as both data sources agree in
identifying these as storms with high rainfall, but would be important to
consider for cases that include rainfall as a continuous measurement."

We have added estimates of these correlations specifically for high-precipitation
events in a new table in the Supplemental Material (Table S1, reproduced 
as Table \@ref(tab:highprecipcorr) of this response document).

\input{tables/precip_high_corr.tex}

### 2020-07-22 ehp_revision/response_to_reviewers.Rmd

\input{tables/precip_high_corr.tex}

\begin{shaded}
\textbf{R2 Comment 4:}
Figure 4: I would add Y-axis label “NOAA classification."
\end{shaded}

**Response:**

This is a great suggestion. We have made this change, as well as several changes
in response to EHP's Request 4 later in this response.

The original and revised versions of Figure 4 of the paper are reproduced in
Figure \@ref(fig:fig4) of this response.

```{r fig4, fig.cap="Reproduction of Figure 4 from the original manuscript (top) and revised version in the resubmitted manuscript (bottom). In the revised version, we have added a title to the y-axis ('Classification based on NOAA Storm Events Data'), binned the values shown by each point's fill, so these colors are easier to distinguish, increased the size of the points, and changed the algorithm for jittering, so none of the points overlap.", fig.show = "hold", fig.align = "center", out.width="100%"}
include_graphics("../figures/floodcomparison.pdf")
include_graphics("figures/floodcomparison.pdf")
```

@@

As we note in our response to EHP Request 2, we used colormaps for all
figures that are designed to be perceptible both for those with common types of
color vision deficiency and when printed in grayscale. We have increased the
size of the circles in Figure 3 of the revised manuscript (reproduced in Figure
\@ref(fig:fig3) of this response) so that the colors are clearer, as well as
truncated the x-axis as requested in EHP Request 1. Also, we show in Figures
\@ref(fig:fig3check1) and \@ref(fig:fig3check2) of this response how the revised
Figure 3 would look with three common types of color vision deficiency as well
as when printed in black and white. The gradient is clear when this figure is
printed in black and white.

```{r fig3check1, fig.cap="Reproduction of revised version of Figure 3 to check accessibility to readers with two types of color vision deficiency, deuteranopia (left) and protanopia (right).", out.width="100%"}
include_graphics("figures/windcomparison_check1.pdf")
```

```{r fig3check2, fig.cap="Reproduction of revised version of Figure 3 to check accessibility to readers with a third type of color vision deficiency, tritanopia (left) and for printing the figure in grayscale (right).", out.width="100%"}
include_graphics("figures/windcomparison_check2.pdf")
```

\begin{shaded}
\textbf{EHP Request 4:}
Figure 4: Even with nominally normal color vision and a large high-resolution
monitor, it is difficult for me to make out the color differences in the
symbols---almost all appear black or very dark blue, a dozen or so look yellow,
and a handful look dark grey. Is there any way to increase the contrast in these
colors? Would you consider binning into categories instead of using a
continuous color gradient?
\end{shaded}

@@

**Response:**

Thank you for these suggestions.

For the original figure, most of the events resulted in 0% of flood gages
exceeding the flood threshold, especially for events that were not recorded as
floods based on NOAA Storm Events. Therefore, most of the points in the original
were indeed dark blue, representing 0%, but we can see that readers might have
questioned if this was the case or if the scale made it harder to see subtler
differences.

We have reproduced both the original and revised versions of Figure 4 as Figure
\@ref(fig:fig4) of this response. We have made several changes to make this
figure easier for readers to see and interpret. These changes include:

- Binning the values shown by the points fill, so that readers only need to 
be able to distinguish among four colors, rather than across a larger scale.
- Increasing the size of the points, so the fill in each point is easier to 
see. 
- Using a different algorithm to "jitter" the points, so there are no points that
overlap each other.

### 2020-07-23 ehp_revision/response_to_reviewers.Rmd

**Response:**

- Differs by exposure metric. Easier for some (wind, rain) than for others (flood, 
tornado)
- For rain, we use a re-analysis product only available for the continental US (right?).
However, there are similar gridded re-analysis products available for other regions 
worldwide that could be used in a similar way.
- For tornadoes, there may be national databases in other spots similar to the tornado
database that we use, but as far as we're aware, no international one. 
- Same for floods. 
- For wind, the wind model could be generalizable with some tweaks. These include: 
  + More landmasks
  + Direction of storm movement for Northern vs Southern Hemispheres
  + Different wind averaging periods for the recorded best tracks data in different 
  storm basins.
  + Our wind model was derived with US data and so may need bias-correction or a shift
  to a West Pacific--based model

> "Tornadoes long have been recognized as a global phenomenon (e.g., Wegener 1917; 
Feuerstein et al. 2005), having been recorded in every continent except Antarctica. 
As such, numerous nationas share an interest in improving assessment of their 
damage. International research and involvement in tornado survey work and damage
and intensity scales is well underway." [@edwards2013tornado]

For flood and tornado events, we used a database of severe weather events that
is specific to the United States (the US NOAA's Storm Events database). To 
expand our exposure data for these hazards internationally, we would need to find
similar databases for other affected countries. 
[international flood and tornado databases? EM-DAT? Others?]

The wind exposure data is based on modeling wind fields based on records of
the storm's track and central intensity throughout the tracking period. These
values are tracked for tropical cyclones around the world, and so it would be
possible to expand the dataset to encompass other countries for wind exposure
measurements. However, there are some practical issues that would need to 
be addressed to do so with the approach we've taken.

The software we are using to model wind [@stormwindmodel] has several features that
make it specific to Atlantic basin storms. First, some steps in the model depend
on whether the storm's center or the location being modeled is over land or water. 
These steps use a landmask---a grid with a binary indicator of land or sea by 
latitude and longitude. Currently, the software only provides a landmask that 
covers the United States, the Gulf of Mexico, and areas of the Atlantic Ocean 
near the US. Second, the model assumes that cyclonic winds are counterclockwise, 
and so is valid only for the Northern Hemisphere. Third, the model assumes that
the central intensity of the storm is based on [wind averaging period], which is 
the standard used in the tracking data for Atlantic-basin storms, but is not
a common standard around the world. Instead, some basins record central intensity
measurements using averaging periods of ....

Therefore, it would be relatively straightforward to expand the wind exposure data
to cover other countries affected by Atlantic-basin storms, although this would 
require some expansion of the area covered by our current landmask. More modifications
would need to be made to the wind model software before it could be extended
to storms in other basins, particularly basins that use different wind averaging 
periods for their main tracking data and basins in the Southern Hemisphere. 
Alternatively, other wind modeling software could be used for this exposure 
assessment, as other groups have developed software that is more extensible to 
multiple storm basins [Australian group's software].

The rain exposure data would also be fairly easy to extend to cover other countries, 
although again there would be a few practical limitations to extend the approach
we've taken in developing the dataset covered in this manuscript. For this exposure, 
we've used a re-analysis dataset. We've taken some steps to translate this gridded data
to the county scale, so it can be integrated with the scale for many human impacts
measurements. However, these steps have been well documents [ref] and would be easy to
reproduce. The re-analysis dataset that we use is specific to the contiguous US [ref
on NLDAS], but other similar re-analysis datasets exist for other locations [example
of one with global coverage?].

For all of these, we have provided exposure assessments at the county scale. Any of the 
steps we have taken could be done for other countries at a similar geopolitical scale, 
although the name of that areal unit will vary by country (e.g., municipalities in Mexico, 
districts in India). For wind and rain exposures, the approach we take here could be
used with any areal unit, as long as there are geographical shape files available for
the area boundaries (although the modeling for wind may be to the area's geographic
mean center rather than population mean center).

> "We initially developed software to model exclusively Atlantic-basin storms
[@tormwindmodel]. There are two characteristics of Northwestern Pacific Ocean
basin storm data that prevent direct use of the current version of the software.
First, the software currently requires Western Hemisphere longitude inputs.
Second, the ``Best Tracks'' data from the China Meteorological Administration
include central tropical cyclone intensity using a 2-minute averaging period,
while the software currently assumes that central intensities are given for a
1-minute averaging period, as is the case for storm track data from the US
National Hurricane Center. With the assistance of Ms. Schumacher, we will update
our tropical cyclone wind model software to appropriately handle 'Best Tracks' data from
the China Meteorological Administration, incorporating conversion factors
[@harper2010guidelines] to convert central storm maximum sustained wind
measurements to a common averaging period prior to applying further steps of the
wind model."

@@

\textit{Lines 164--166 from original manuscript:}

\begin{quotation}
\noindent
\textit{"They found important differences, concluding that a study may be prone
to bias from exposure misclassification if distance to the storm track is used
as a proxy for exposure (Grabich et al. 2015a)."}
\end{quotation}
\end{shaded}

**Response:**

It is obvious that it is typically better, but in cases where the proxy is much more
practical to measure, it may need to be more than just a bit better, but 
instead substantially better. Also, there could be some cases where the proxy 
might actually be better---for example, if the proxy can be measured with 
very low level, while the direct exposure measure might only be measurable 
with high error. In that case, the proxy could be the better metric and might
provide a more precise estimate of the association with health risk.

[Env. Epi. book---advantages and disadvantages of different types of measures]

We agree that it is helpful to clarify for readers that these independent hazards
can come together in a storm event at different intensities and at different time
windows. We have added some text on this:

[Added text]

However, we disagree that this should be down as an alternative to calculating
agreement. Epidemiologists need to understand how these exposure measurements
agree to help in planning studies and statistical approaches to interpreting the
resulting data. In this sense, "agreement" is providing a measure similar to
correlation for continuous variables; our choice of agreement with the binary
exposure classifications reflects the more common use of binary classifications
for most tropical cyclone epidemiology to date.

Epidemiological studies might focus on tropical cyclone exposures at two levels.
First, they might wish to focus on a specific hazard. For example, a study might
hypothesize that mold growth following flooding from a tropical storm might
increase risk of respiratory health outcomes in the months after a storm. In
this case, the clear causal pathway recommends a focus on one of the storm
hazards, rather than all storm hazards. However, other storm hazards could
confound the association between flood exposure and respiratory health risk if
the other hazards are ignored *and* if they are associated with both the
exposure of interest (storm-associated flooding) and the health outcome. For
example, if wind exposure assessments are in high agreement with flood exposure
assessments for storms, and if wind affects risk of respiratory outcomes by
causing extensive property damage and creating extreme psychological stress,
which can have repercussions on respiratory health, then the wind hazard could
confound the estimated association between storm-related flood exposure and the
health outcome.

This bias would be higher when the confounder and exposure of interest are more
strongly correlated (for continuous variables) or in higher agreement (for
categorical variables). Conversely, if the exposure and the potential confounder
are, in practice, only weakly associated, then the potential for confounding is
low. The Jaccard index is one measure of similarities between categorical
(including binary) coefficients.

Another consideration is collinearity. If one hazard is the exposure of interest
and another hazard is a potential confounder, then the model should adjust the
confounder or it will be misspecified and be prone to bias. However, if the 
exposure of interest and the potential confounder are very strongly correlated/in
agreement, then including both as independent variables in a regression model
often causes numerical problems in fitting the regression model, including 
instability in the estimated coefficients and inflated variance. In very extreme
cases, the statistical software may not be able to invert the matrix [? only for
linear regression?].

Therefore, it is helpful for epidemiologists to understand if these independent
storm-associated hazards tend to be strongly associated (in high agreement), 
both within specific storms (for single-storm studies) and on average across
most large storms (for multi-storm studies). This knowledge will help them in 
identifying potential confounders if they are interested in studying the 
effects of a single hazard of the storm and also in determining if control for
these potential confounders among other storm hazards might cause numerical 
problems or other collinearity-associated problems when fitting a regression 
model.

If a researcher wishes to study the storm as a whole, then the researcher 
could either seek a single measure to capture exposure to the storm as a whole
or investigate more complex models that model the influence of the storm through
pathways of several different hazards.

If a researcher wants a single measure for the storm as a whole, then it is helpful
to know how well exposure assessments based on the hazard components of the storm
agree with each other. If there is strong agreement, then any of those hazards could
be used as a primary marker of exposure assessment. This is conceptually similar to 
checking for observer / rater agreement.

> "When the row and column variable srepresent different observers' rating the same
subjects or objects, interest is focused on *observer agreement* rather than mere 
association. In this case, measures and tests of agreement provide a method of
assessing the reliability of a subjective classification or assessment procedure."
[@friendly2015discrete]

> "In assessing the strength of *agreement* we usually have a more stringent 
criterion than in measuring the strength of *association*, because observers 
ratings can be strongly associated without strong agreement. For example, one
rater could use a more stringent criterion and thus consistently rate subjects
one category lower (on an ordinal scale) than another rater. More generally, 
measures of agreement must take account of the marginal frequencies with which two 
raters use the categories. If observers tend to use the categories with different
frequency, this will affect measures of agreement." [@friendly2015discrete]

When you have an array of two or more exposures that are strongly correlated, 
including them together in a regression model can cause problems from collinearity
[@schisterman2017collinearity].

> "Environmental exposures ... often consist of an array of related individual 
factors that may be highly correlated with each other, causing concern about the
impact of collinearity when attempting to identify individual effects." [@schisterman2017collinearity]

**Commonly have multiple factors of interest, correlated**

In some areas of epidemiology, researchers have moved toward the idea of a 
"web of causality":

> "'Multiple causation' is the canon of contemporary epidemiology, and its
metaphor and model is the 'web of causation'. Expressed through the notion
of 'multifactorial etiology' and embedded in the statistical techniques
of 'multivariate analysis', the belief that population patterns of health 
and disease can be explained by a complex web of numerous interconnected 
risk and protective factors has become one of this discipline's central 
concepts. Equally entrenched is the corrolary that epidemiology's power
to improve the public's health rests upon its ability to identify---and predict
the results of breaking---selected strands of this causal web." [@krieger1994epidemiology]

This is in contrast to focusing on single factors:

> "Expressly challenging the still-pervasive tendency of epidemiologists to think
in terms of single 'agents' causing discrete diseases, the provocative metaphor
and model of the 'web' invited epidemiologists to embrace a more sophisticated
view of causality." [@krieger1994epidemiology]

In this framework, epidemiology helps by identifying where it would help to
break strands of the web:

> "Using this model, MacMahon et al. drew several important inferences about
prevention and research that remain part of epidemiologic thinking to this 
day. Arguing that 'to effect preventative measures, it is not necessary to 
understand causal mechanisms in their entirity', they stated that 'even knowledge
of one small component may allow some degree of prevention' since 'wherever the
chain is broken the disease will be prevented'." [@krieger1994epidemiology]

In other words, if you can identify *necessary* causes, you can craft 
*practical* interventions.

In some fields of epidemiology (e.g., nutritional epidemiology), it is common 
to study cases where there are multiple potential risk factors, and these 
factors are often strongly correlated [@schisterman2017collinearity].

> "The dynamics of many important ecological and evolutionary processes are 
often influenced by multiple interacting factors, and attempting to understand 
the dynamics of such systems presents difficult technical and philosophical 
problems." [@petraitis1996inferring]

> "Often in practice, investigators are faced with decisions of how to handle
highly correlated variables." [@schisterman2017collinearity]

**Methods to tackle multiple causality**

When the aim is to explore the influences of multiple associated factors, there
are some different strategies that can be used. These include multiple regression
and path analysis:

> "Evolutionary ecologists have recently turned to path analysis, multiple regression,
and related techniques to analyse systems of multiple causality. While these
techniques are often seen as competitors, they are, in fact, related, and as a 
result the problems of these techniques are similar." [@petraitis1996inferring]

**Implications of collinearity**

> "Two variables are defined as collinear if one can be expressed as an exact
or near linear combination of the other. ... In general, collinearity between
variables is described by the magnitude of their correlation." 
[@schisterman2017collinearity]

It can complicate inference of model coefficients. This is always a concern for 
inferential models. For predictive models, it can be a problem if you later use
the model to predict in a case where the correlation structure is different than
in the training data.

> "The dependence of regression and path coefficients on the correlation structure
is often glossed over. Yet this dependence means that inferences about the strengths
of path coefficients are conditional upon the correlational structure among the 
predictor variables. If the correlation structure of the sample does not
match the correlational structure of the population then regression and path 
coefficients will not estimate relative strengths accurately. This can occur if
sampling is not random or if analysis is based on data from experiments with 
factorial designs, which break the correlational structure amnog the predictor
variables." [@petraitis1996inferring]

These implications can depend on whether the modeling goal is predictive or 
inferential.

> "When the goal is to choose covariates based on their predictive value, 
concerns about collinearity stem from the desire to improve parameter estimates'
precision, which can be inflated when highly correlated covariates are included
in the model." [@schisterman2017collinearity]

> "In a causal framework, on the other hand, interest is often centered on a
specific effect from a correctly specified causal model, even in the presence of
highly correlated data, despite a potential loss of statistical efficiency.
Under such a viewpoint, bias due to misspecification of the causal associations
is a more devastating result than reduced precision of parameter estimates
correctly estimated. Furthermore, a precisely but incorrectly estimated
parameter may lead to invalid inferences. ... Relying on conventional
variable-selection algorithms and standard analyses can ignore important
confounders and even produce extremely imprecise confidence intervals."
[@schisterman2017collinearity]

The amount of bias in the unadjusted model (in terms of bias from an unadjusted
confounder) depends on the strength of association between the exposure of
interest and the potential confounder [@schisterman2017collinearity].

> "This is especially important for the confounding variable scenario, where 
correctly specifying the model may result in adjusting for a nearly 
collinear variable." [@schisterman2017collinearity]

The degree of agreement will influence the degree of confounding in an 
unadjusted model, for either one or two confounders:

> "In this confounding scenario, increasing correlation exacerbates the bias
due to misspecification, similar to results for a single confounder."
[@schisterman2017collinearity]

Extreme collinearity can create numerical problems [@schisterman2017collinearity].

> "Under the extremely unlikely scenario of extreme collinearity [(abs. rho of 0.999 
or higher)], the numerical matrix inversion required for estimation fails, resulting
in unstable and biased predictors." [@schisterman2017collinearity]

> "Only for extreme values of rho cloes to 1 or -1 is beta-squareed nonidentifiable
due to numerical instability; otherwise, the correctly specified model produces
the most desirable (e.g., unbiased) estimates of the total effect of the exposure
on the outcome." [@schisterman2017collinearity]

Collinearity can cause imprecision in coefficient estimates, even if those
estimates are unbiased [@schisterman2017collinearity].

**Techniques to address collinearity**

There are study designs that might help to separate different effects. For example, 
some matching designs might help in creating a subset of data in which the association 
that exists in the full dataset is broken (e.g., @leal2012multicollinearity).

> "Matching is typically employed to reduce model dependence and estimate 
associations in a more empirical way than would be necessary without 
matching. In line with this practice, matching was employed as a diagnostic
tool to verify whether the effects of environmental variables that are highly 
correlated with each other could be disentangled." [@leal2012multicollinearity]

You could also explore techniques of dimension reduction, to create a smaller
subset of independent variables for which the correlation is broken. For example, 
you could use PCA [@leal2012multicollinearity].

There are other techniques that allow some bias in estimates in an attempt to reduce
problems from collinearity, like ridge regression [@petraitis1996inferring].

> "Several biased estimation techniquest ahve been proposed as a way to combat
collinearity (Myers 1990). These are controversial methods. Ridge regression, for
example, biases the regression coefficients in order to improve the model's 
ability to predict the criterion variable. The estimates of the individual regression
coefficients may be very biased even though when taken together they provide a 
very good prediction of the criterion variable." [@petraitis1996inferring]

> "When correct specification of the models still leads to 
problems for conventional regression methods, one can apply modern techniques
such as Bayesian hierarchical models with shrinkage estimators."
[@schisterman2017collinearity]

**Are effects of different factors 'separable'?**

Epidemiology often aims to inform policy decisions. In this case, it can be important
to characterize the separate effects of different associated factors that contribute
to the health risk [@leal2012multicollinearity].

> "To develop efficient public health interventions addressing the obesity 
epidemic, it is important to identify exactly which aspects of the
environment influence obesity risk. For example, demonstrating that the density 
of fast-food restaurants was associated with obesity risk and demnstrating that
the density of sports facilities was associated with obesity risk would lead to 
different interventions." [@leal2012multicollinearity]

However, it can be very difficult to separate the effects of different factors
if those factors are strongly correlated [@leal2012multicollinearity]:

> "However, many neighborhood characteristics, especially those related to the 
densities of physical features and services, are strongly correlated with 
each other. Therefore, it is not clear whether it is even possible to disentangle
the effects of these different environmental dimensions, even if they are hypothesized
to influence obesity risk through distinct causal pathways." [@leal2012multicollinearity]

### 2020-08-09 ehp_revision/tables/precip_high_corr.tex
Work some more on revision

\caption{\label{tab:highprecipcorr}Precipitation correlation during all versus high-precipitation events.
                     The same sample of counties is shown as in Figure ... of the main text.
                     Events are cases where a tropical cyclone came within ... km of each of the 
                     listed counties. The number of total events gives the sum of all points
                     shown on the main plot for the county in Figure ... of the main text. 
                     The Spearman correlation for all events is the same as that shown in Figure ...
                     of the main text. High-precipitation events are those for which storm-associated
                     precipitation was 75 mm or higher based on at least one of the two measures
                     considered in this comparison (NLDAS and monitors). The Spearman correlation
                     for these high-precipitation events is given in the last column of the 
                     table.}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{All events} & \multicolumn{2}{c}{High-precipitation events} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
County & \makecell[c]{Number\\of events} & \makecell[c]{Spearman\\correlation} & \makecell[c]{Number\\of events} & \makecell[c]{Spearman\\correlation}\\
\midrule
Miami-Dade, FL & 65 & 0.94 & 18 & 0.49\\
Harris, FL & 38 & 0.93 & 10 & 0.84\\
Mobile, AL & 50 & 0.95 & 20 & 0.57\\
Orleans, LA & 55 & 0.89 & 13 & 0.95\\
Fulton, GA & 48 & 0.95 & 12 & 0.69\\
\addlinespace
Charleston, SC & 73 & 0.94 & 17 & 0.65\\
Wake, NC & 61 & 0.98 & 12 & 0.84\\
Baltimore, MD & 33 & 0.92 & 5 & 0.70\\
Philadelphia, PA & 52 & 0.96 & 6 & 0.77\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:highprecipcorr}Precipitation correlation during all versus high-precipitation events.
                     The same sample of counties is shown as in Figure 2 of the main text.
                     Events are cases where a tropical cyclone came within ... km of each of the 
                     listed counties. The number of total events gives the sum of all points
                     shown on the main plot for the county in Figure 2 of the main text. 
                     The Spearman correlation for all events is the same as that shown in Figure 2
                     of the main text. High-precipitation events are those for which storm-associated
                     precipitation was 75 mm or higher based on at least one of the two measures
                     considered in this comparison (NLDAS and monitors). The Spearman correlation
                     for these high-precipitation events is given in the last column of the 
                     table.}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{All events} & \multicolumn{2}{c}{High-precipitation events} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
County & \makecell[c]{Number\\of events} & \makecell[c]{Spearman\\correlation} & \makecell[c]{Number\\of events} & \makecell[c]{Spearman\\correlation}\\
\midrule
Miami-Dade, FL & 65 & 0.94 & 18 & 0.49\\
Harris, TX & 38 & 0.93 & 10 & 0.84\\
Mobile, AL & 50 & 0.95 & 20 & 0.57\\
Orleans, LA & 55 & 0.89 & 13 & 0.95\\
Fulton, GA & 48 & 0.95 & 12 & 0.69\\
\addlinespace
Charleston, SC & 73 & 0.94 & 17 & 0.65\\
Wake, NC & 61 & 0.98 & 12 & 0.84\\
Baltimore, MD & 33 & 0.92 & 5 & 0.70\\
Philadelphia, PA & 52 & 0.96 & 6 & 0.77\\
\bottomrule
\end{tabular}
\end{table}

### 2020-08-09 ehp_revision/writing/ehp_discussion.tex
Work some more on revision

The open-source data generally correspond well with data from other potential
sources (Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison}), but
there are caveats. The rainfall data are generally well-correlated with
ground-based observations, but may sometimes underestimate very high rainfall
values (Figure~\ref{fig:raincomparison}). When rainfall data is used to create
binary exposure classifications, this disagreement is unlikely to influence
results, as both data sources agree in identifying these as storms with high
rainfall, but would be important to consider for cases that include rainfall as
a continuous measurement.

@@

We did find a small set of tropical cyclones for which for which
agreement was high across several single-hazard exposure assessments (e.g.,
Floyd in~1999, Irene in 2011, Hannah in~2008, Bertha in~1996; Ernesto in~2006
(Figure~\ref{fig:jaccard})).  Hurricanes Floyd in~1999 and Irene in~2011 both
made their first \ac{US} landfall in North Carolina at minor hurricane
intensity (Category~2 and~1, respectively) and then skimmed the eastern coast
of the \ac{US} north through New England, bringing substantial rainfall to much
of the eastern coast from North Carolina north and causing extensive inland
flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008, Bertha in~1996, and Ernesto in~2006 also followed the eastern
coastline. For these storms, the tropical cyclones' persistent proximity to
water may have helped maintain wind speeds in similar patterns to rain and
distance-based exposures, resulting in more similarities across
exposure assessments compared to other tropical cyclones.  For these storms, it
may be possible to assess exposure to multiple hazards of the storm using a
single metric, perhaps even a proxy like the distance between the county
and the storm's track.  However, for these storms it may be difficult to
untangle the contribution of each hazard to the overall effect of the storm,
given that several hazards have similar geographical patterns.

>>>>

The open-source data generally correspond well with data from other potential
sources (Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison}), but
there are caveats. The rainfall data are generally well-correlated with
ground-based observations, but may sometimes underestimate very high rainfall
values (Figure~\ref{fig:raincomparison}), and in some counties the correlation
was substantially lower when considering only tropical cyclones with cumulative
local rainfall of 75 mm or more (Supplemental Table 1). When rainfall data is
used to create binary exposure classifications, this disagreement is unlikely
to influence results, as both data sources agree in identifying these as storms
with high rainfall, but would be important to consider for cases that include
rainfall as a continuous measurement.

@@

We did find a small set of tropical cyclones for which for which agreement was
high across several single-hazard exposure assessments (e.g., Floyd in~1999,
Irene in 2011, Hannah in~2008, Bertha in~1996; Ernesto in~2006
(Figure~\ref{fig:jaccard})).  Hurricanes Floyd in~1999 and Irene in~2011 both
made their first \ac{US} landfall in North Carolina at minor hurricane
intensity (Category~2 and~1, respectively) and then skimmed the eastern coast
of the \ac{US} north through New England, bringing substantial rainfall to much
of the eastern coast from North Carolina north and causing extensive inland
flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008, Bertha in~1996, and Ernesto in~2006 also followed the eastern
coastline. For these storms, the tropical cyclones' persistent proximity to
water may have helped maintain wind speeds in similar patterns to rain and
distance-based exposures, resulting in more similarities across exposure
assessments compared to other tropical cyclones.  For these storms, it may be
possible to assess exposure to multiple hazards of the storm using a single
metric, perhaps even a proxy like the distance between the county and the
storm's track. \textbf{With the dataset we describe in this paper, however,
there is little need to limit analysis based on exposure to a single hazard or
proxy, although multi-hazard studies of storms with high agreement among hazard
exposures should look out for modeling issues from multicollinearity.} Further,
for these storms it may be difficult to untangle the contribution of each
hazard to the overall effect of the storm, given that several hazards have
similar geographical patterns.
